
\chapter*{Acknowledgement}

This semester thesis was initiated by the Swiss Federal Railway Operator SBB at the Power Systems Laboratory at ETH Zürich. 
Initially I was not planning to do a semester thesis this spring. However, once when scrolling on the PSL homepage I saw the description of this thesis. I directly knew, that I really wanted to do this, since railways and power systems are my core interests during my studies. And looking back, it was totally worth it to change my plans. I had a lot of fun doing this work and drew many learnings for future works out of it. 


First of all I would like to thank Prof. Hug to give me the opportunity to write this thesis at the power systems laboratory. 


Next I want to thank my supervisor at ETH, Han Xuejiao, who strongly supported me during this thesis. She was always open to my questions, she even took the time to skype when she was on vacation or on conferences. Moreover, she also pushed me many times to think myself about a better solution. Thanks Jo, for always being available to my questions. 


Furthermore, I would like to thank Josep Aniceto, who was one of my supervisors at SBB. He always expressed his support and appreciation for my work. And although he had many things to do, he always replied to my questions as quickly as possible or he even took the time to meet in person several times. Thank you Josep for supporting me with your experience and advice , which sometimes went beyond the content of this thesis. 


Many thanks also to Julius Bosch, another supervisor at SBB, who helped a lot with initiating this thesis. He gave me many useful inputs and always replied quickly to my questions.  


Last but not least, a warm thank to my dear friend Patrick Althaus, who was always there for me whenever the simulations did not work as I expected or when I was losing track of things due to the high workload I had parallel to this thesis.